Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
%
To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster}.
%
The experiemental results on other datasets were similar.
%
We used the same hyper-parameters for the sample-based training and the full-batch training.
%
For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy for the full-batch training, according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.

>>>>

Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
%
To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes.
%
\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} compare their accuracy with the cases that we used the full graph participated in the training.
%
For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.
